Relationships in the extremes and their influence on competition and coexistence: Supporting information

### 2021-09-29 paper/SupMat.Rnw
finished editing for now, through the Results, but no Discussion yet

We created two cases for $(b_1,b_2)$, left- and right-tail association. 
To generate $M$ points $\left(b_1^{(i)}, b_2^{(i)}\right)$, $i=1,..,M$, for the left tail association case, we first generated M points $(a_1^{(i)},a_2^{(i)})$, $i=1,...,M$, from a bivariate normal distribution $N\left( \vec{0}, \Sigma \right)$, where here $\Sigma = \begin{pmatrix} 1&0\\0&1\end{pmatrix}$. 
Then, for each index $i$, we randomly, with 50\% probability, either (A) let $\tilde b_1^{(i)} = -|a_1^{(i)}|$ and $\tilde b_2^{(i)} = -|a_1^{(i)}|$, or (B) let $\tilde b_1^{(i)} = |a_1^{(i)}|$ and $\tilde b_2^{(i)} = |a_2^{(i)}|$. 
We then let $b_1^{(i)} = \sigma \tilde b_1^{(i)} + \mu_1$ and $b_2^{(i)} = \sigma \tilde b_2^{(i)} + \mu_2$. 
Perfect association in the left tails of the resulting distribution $\left(b_1,b_2\right)$ results from the fact that, in case (A) above, both $\tilde b_1^{(i)}$ and $\tilde b_2^{(i)}$ were assigned to the same value. 
For speed of computation, when samples $(b_1^{(i)},b_2^{(i)})$, $i=1,...,M$ were needed for distinct sets of values of the parameters $\mu_1$, $\mu_2$, and $\sigma$, we used the same $\left(\tilde b_1^{(i)},\tilde b_2^{(i)}\right)$, $i=1,...,M$, simply transforming these values differently (using the different valus of $\mu_1$, $\mu_2$, $\sigma$) for each set of parameter values. Right-tail associated noise was generated in an analogous way. 
Overall, our version of the lottery model was completely specified by specifying $\delta$, $\mu_1$, $\mu_2$, $\sigma$ and whether 
noise was generated from the left- or right-tail association cases.

When needed, noise with symmetric tail association was generated by taking a very large sample (\Sexpr{M}) 
%***DAN: Dan, later, check whether 100000 is what was actually used. I'm thinking we could probably do a million.
of left-tail associated noise generated as 
described above, and then calculating the Pearson correaltion coefficient, $\rho$, of the sample.
Symmetric noise $\left(\tilde b_1^{(i)},\tilde b_2^{(i)}\right)$ for $i=1,...,M$ was then generated 
from the bivariate normal distribution $N\left(\vec{0}, \Sigma \right)$, where $\Sigma = \begin{pmatrix} 1&\rho \\ \rho&1\end{pmatrix}$, 
and then we set $b_1^{(i)} = \sigma \tilde b_1^{(i)} + \mu_1$ and $b_2^{(i)} = \sigma \tilde b_2^{(i)}+ \mu_2$.

>>>>

We created two cases for $(b_1,b_2)$, left- and right-tail association. 
To generate $M$ points $\left(b_1^{(i)}, b_2^{(i)}\right)$, $i=1,..,M$, for the left tail association case, we first generated M points $(a_1^{(i)},a_2^{(i)})$, $i=1,...,M$, from a bivariate normal distribution $N\left( \vec{0}, \Sigma \right)$, where here $\Sigma = \begin{pmatrix} 1&0\\0&1\end{pmatrix}$. 
Then, for each index $i$, we randomly, with 50\% probability, either (A) let $\tilde b_1^{(i)} = -|a_1^{(i)}|$ and $\tilde b_2^{(i)} = -|a_1^{(i)}|$, or (B) let $\tilde b_1^{(i)} = |a_1^{(i)}|$ and $\tilde b_2^{(i)} = |a_2^{(i)}|$. 
We then let $b_1^{(i)} = \sigma \tilde b_1^{(i)} + \mu_1$ and $b_2^{(i)} = \sigma \tilde b_2^{(i)} + \mu_2$. 
Perfect association in the left tails of the resulting distribution $\left(b_1,b_2\right)$ results from the fact that, in case (A) above, both $\tilde b_1^{(i)}$ and $\tilde b_2^{(i)}$ were assigned to the same value. 
For speed of computation, when samples $(b_1^{(i)},b_2^{(i)})$, $i=1,...,M$ were needed for distinct sets of values of the parameters $\mu_1$, $\mu_2$, and $\sigma$, we used the same $\left(\tilde b_1^{(i)},\tilde b_2^{(i)}\right)$, $i=1,...,M$, simply transforming these values differently (using the different valus of $\mu_1$, $\mu_2$, $\sigma$) for each set of parameter values. Right-tail associated noise was generated in an analogous way.

When needed, noise with symmetric tail association was generated by taking a very large sample (\Sexpr{M}) 
of left-tail associated noise generated as 
described above, and then calculating the Pearson correaltion coefficient, $\rho$, of the sample.
Symmetric noise $\left(\tilde b_1^{(i)},\tilde b_2^{(i)}\right)$ for $i=1,...,M$ was then generated 
from the bivariate normal distribution $N\left(\vec{0}, \Sigma \right)$, where $\Sigma = \begin{pmatrix} 1&\rho \\ \rho&1\end{pmatrix}$, 
and then we set $b_1^{(i)} = \sigma \tilde b_1^{(i)} + \mu_1$ and $b_2^{(i)} = \sigma \tilde b_2^{(i)}+ \mu_2$.

Overall, our version of the lottery model was completely specified by specifying $\delta$, $\mu_1$, $\mu_2$, $\sigma$ and whether 
noise was generated from the symmetric, left- or right-tail associated cases.
